Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-22 latex/article.tex
typo

\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1,2}\and David
Coeurjolly\inst{1}\and Jean-Philippe Farrugia\inst{1}\and Jean-Claude
Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{2} }

>>>>

\author{H\'el\`ene Perrier\inst{1}\and J\'er\'emy Levallois\inst{1,2}\and David
Coeurjolly\inst{1}\and Jean-Philippe Farrugia\inst{1}\and Jean-Claude
Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{2} }
